Output Summary

### 2022-04-05 03-post-process/output-plots.Rmd

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "size-based-surv-growth-relationship"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---
